### 2017-11-21 Docs/Thesis/docs/chapter6.tex
update on ch6

In this section, we discuss some ideas for future works and implementation for SIMITAR. We suggest approaches to get better results. They include performance improvements, calibration of constants\footnote{Calibration here means to test many values, and see which one can improve our outcomes for a large variety of traces of traces.} and a finer control of packet injection. We list them as a task list on the table ~\ref{tab:task-list}.

\begin{table}[ht!]
	\centering
	\caption{Future Work: task list}
	\label{tab:task-list}
	\begin{tabular}{cccc}
		\hline
		\multicolumn{3}{c}{Future Work}	& Priority \\ \hline
		1                      & Optimizing linear regression                              &                                                 & \textit{high}                    \\
		2                      & Flow-merging option                                       &                                                 & medium                  \\
		3                      & Smart flow-scheduler                                      &                                                 & \textit{high}                    \\
		4                      & \texttt{DataProcessor::minimumAmountOfPackets}                         &                                                 & low                     \\
		5                      & DPDK KNI interfaces                                       &                                                 & low                     \\
		6                      & Multi-thread C++ sniffer                                  & \multirow{-6}{*}{Performance}                   & \textit{high}                    \\ \hline
		7                      & Model inter-packet times on \texttt{TinsFlow}           &                                                 & \textit{high}                    \\
		8                      & D-ITG flow generator (\texttt{DitgFlow})                &                                                 & low                     \\
		9                      & DPDK flow generator (\texttt{DpdkFlow})                 &                                                 & medium                     \\
		10                     & Ostinato flow generator (\texttt{OstinatoFlow})         & \multirow{-4}{*}{Tool support}                  & low                     \\ \hline
		11                     & \texttt{DataProcessor::min\_time}                       &                                                 & low                     \\
		12                     & \texttt{DataProcessor::m\_min\_on\_time}                &                                                 & low                     \\
		13                     & \texttt{DataProcessor::m\_session\_cut\_time}           &                                                 & low                     \\
		14                     & Minimum number of packets per flow option                 & \multirow{-4}{*}{Calibration}  & low                     \\ \hline
		15 & Python API/Lua for traffic generation & & low \\
		16 & Crafter of  pcap files & \multirow{-2}{*}{New features} & low \\
		%17 & Json compact trace descriptor  & \multirow{-3}{*}{New features} & low 
		\hline
	\end{tabular}
\end{table}

@@

In this dissertation we discuss our process of conceiving, researching, definition and development and validation of an realistic traffic generator able to at the same time fulfill gaps others proposals haven't, and achieve results comparable to the available proposals. This was not a linear procedure. Was indeed anespiral procedure, as proposed by Sommervile on Software Engineering\cite{sommerville}. At the figure~\ref{fig:spiral} we show how it was done.

@@

Starting with some concepts, we search in the literatue the state of things, related works and some gaps for inovation. We proposed a traffic generator, and validated a simplistic prototype \footnote{In the appendix ~\ref{ap:publications}, the  article "Towards a Flexible and Extensible Framework for Realistic Traffic Generation on Emerging Networking Scenarios" where this prototype is validated is presented.} \footnote{This initial step was crucial, since on later stages, changes on the architecture design are much more dificult. In fact, some ponctual changes such as directory structure and new classes are inevitable. But structural changes are impracticable.}. After this we serch for more sollutions and methodologies that could be applied to solve or problem. In this procedure we researched many topics that at end didnt fit to our intentions, such as Machine Learning and Neural Networks. But others such as Linear regression, maximum likelihood, and BIC and AIC were indeed sactisfatory. Again, we planned a methodology, a procedure, and validate these ideais, as prototypes. Here the seed for the first part of the chapter ~\ref{ch:modeling-evaluation} and the article "Using BIC and AIC for Ethernet traffic model selection. Is it worth?"(at appendix ~\ref{ap:publications}. Than we reseach for more related works to  gain insights and find platforms and lybraries able to fulfill our requirements. In this step we designed our algorithms presented on chapter ~\ref{ch:modeling-evaluation}, and choosed the APIs, packages and lybraries. This procedure continued by incremental upgrades, until we arrived on the version presented on the chapter ~\ref{ch:validation}.

- revisitar as contribuições e os resultados alcançados, e comparar com a literatura

- paragrafo de encerramento

>>>>

With the work done so far and the results achieved, we may identify the current limitation of our project, and plan improvements to solve these issues. 
We can list as  main weak points right now:

\begin{itemize}
	\item Poor performance of the Trace Analyzer and Sniffer components;
	\item Weak scaling results of the traffic generator using \textit{libtins}.
\end{itemize}

And as further implementations, but with low priority, we may have:

\begin{itemize}
	\item Support for new traffic generator tools;
	\item APIs for the Flow Generator on  Python and Lua, wich have cosolidate traffic generator APIs;
	\item A \textit{pcap-crafter} component. Instead of creating traffic, creates a \textit{pcap} file.
\end{itemize}

Identified these issues and possible future works, we conceived approaches and methods to achieve these results. They include improvements on the implementation,  calibration of constants\footnote{Calibration here means to test many values, and see which one can improve our outcomes for a large variety of traces of traces.}, a finner control of packet injection, use of new technologies and newer implementations. As we always did in the project, we create a task list of activities and organize them by priority and goal. They are listed in the table ~\ref{tab:task-list}.

\begin{table}[ht!]
	\centering
	\caption{Future Work: task list}
	\label{tab:task-list}
	\begin{tabular}{cccc}
		\hline
		\multicolumn{3}{c}{Future Work}	& Priority \\ \hline
		1                      & Optimizing linear regression                              &                                                 & \textit{high}                    \\
		2                      & Flow-merging option                                       &                                                 & medium                  \\
		3                      & Smart flow-scheduler                                      &                                                 & \textit{high}                    \\
		4                      & \texttt{DataProcessor::minimumAmountOfPackets}                         &                                                 & low                     \\
		5                      & DPDK KNI interfaces                                       &                                                 & medium                     \\
		6                      & Multi-thread C++ sniffer                                  & \multirow{-6}{*}{Performance}                   & \textit{high}                    \\ \hline
		7                      & Model inter-packet times on \texttt{TinsFlow}           &                                                 & \textit{high}                    \\
		8                      & D-ITG flow generator (\texttt{DitgFlow})                &                                                 & low                     \\
		9                      & DPDK flow generator (\texttt{DpdkFlow})                 &                                                 & medium                     \\
		10                     & Ostinato flow generator (\texttt{OstinatoFlow})         & \multirow{-4}{*}{Tool support}                  & low                     \\ \hline
		11                     & \texttt{DataProcessor::min\_time}                       &                                                 & low                     \\
		12                     & \texttt{DataProcessor::m\_min\_on\_time}                &                                                 & low                     \\
		13                     & \texttt{DataProcessor::m\_session\_cut\_time}           &                                                 & low                     \\
		14                     & Minimum number of packets per flow option                 & \multirow{-4}{*}{Calibration}  & low                     \\ \hline
		15 & Python API/Lua for traffic generation & & low \\
		16 & Crafter of  pcap files & \multirow{-2}{*}{New features} & low \\
		%17 & Json compact trace descriptor  & \multirow{-3}{*}{New features} & low 
		\hline
	\end{tabular}
\end{table}

@@

In this dissertation we discuss our process of conceiving, researching, definition and development and validation of an realistic traffic generator able to at the same time fulfill gaps others proposals haven't, and achieve results comparable to the available proposals. This was not a linear procedure. Was indeed an espiral procedure, as proposed by Sommervile on Software Engineering\cite{sommerville}. Clealy its not identical, because we adapt it for research purposes. At the figure~\ref{fig:spiral} we show a diagram of who  it was done.

@@

Starting with some concepts and ideias, we started definin our goals, and to do so, a task list. The concepts and the task lists were organized on "Working Plan" documents. These tasks lists covered the whole process, and included reserch, study of new subjects, implementation and testing. Next, search in the literatue the state of things, related works and some gaps for inovation. At this point we defined the concepts of our traffic generator according to gaps the state of things we find in the literature. Then we create an architecture model using UML, defining the software components, classes and sequence diagrams. This initial step was crucial, since on later stages, changes on the architecture design are much more dificult. In fact, some ponctual changes such as directory structure and new classes are inevitable. But structural changes are impracticable. At this point we implemented a simplistic prototype, and validate it\footnote{In the appendix ~\ref{ap:publications}, this prototype is validated in the article "Towards a Flexible and Extensible Framework for Realistic Traffic Generation on Emerging Networking Scenarios"}.

After this we serch for more sollutions and methodologies that could be applied to solve or problems and improove the performance of ou prototype. In this procedure we researched many topics that at end didn't fit to our intentions, such as Machine Learning and Neural Networks. But others such as Linear regression, maximum likelihood, and information criterions (BIC/AIC) were indeed sactisfatory. Again, we planned a methodology, a procedure, and validate these ideais, as prototypes. Here the seed for the first part of the chapter ~\ref{ch:modeling-evaluation} and the article "Using BIC and AIC for Ethernet traffic model selection. Is it worth?"(at appendix ~\ref{ap:publications}. Than we reseach for more related works to  gain insights and find platforms and lybraries able to fulfill our requirements. In this step we designed our algorithms presented on chapter ~\ref{ch:modeling-evaluation}, and choosed the APIs, packages and lybraries, such as Armadillo\cite{armadillo}, a C++ linear algebra lybrary. Many ideas we used to conceive our ideas were inspired on previous works and sollutions, such as Harpoon\cite{harpoon-validation}, sourcesOnoff \cite{sourcesonoff-paper} and LegoTG\cite{legotg-paper}. This procedure continued by incremental upgrades, until we arrived on the version presented on the chapter ~\ref{ch:validation}.

In the chapter ~\ref{ch:modeling-evaluation} we achieve a major contribution of our work, that is show that the information criterias AIC and BIC are efficient analyctial methodos for select models for inter-packet times. Both are able infer a good model, even evaluated according different types of metrics, without any type of simulation. Also we show evidence that for Ethernet traffic of data, choosing AIC and BIC make almost no difference. As far as is our knowleadge, this is the most complete study on the use of AIC and BIC on inter-packet times modelling of Ethernet traffic.

At the end, we were able to implement a functional implementation of solution proposed in the chapter ~\ref{ch:introduction}. Our main contrubution here is the development of a traffc generator tool that at the same time is able to provide realistic synthetic traffic, and its modelling framework is extensible for most of the traffic generation lybraries and tools. In fact, our current implementations use tow very distinct packet-crafters: \textit{libtins}, a C++ library designed for the implementation of sniffers and traffic generators, and Iperf, a traffic generator commonly used to measure bandwidth.

Out tests performed on the chapter ~\ref{ch:validation} intend to focous on packet-level, flow-level and scalling metrics, as we state on chapter ~\ref{ch:ch:literature-review}. The results were notably good at the flow level. SIMITAR were able to replicate the flow-cumulative distribution with high acurracy, and with \textit{libtins}, the number of flows as well. The number of flows were larger, because it establishes aditional connections for signaling and statistics control. On scalling and packet matrics, the results still have to be improved. Iperf as the traffic generator tool, still being limited, has prooved to be efficient on replication the scalling characteristics for the Skype traffic. Since it estrablishes socket connections to generate the traffic, we believe that this fact make it and acurate on replication traffic from applications.

Finally, we created a list of improovments and future works, aiming the improovment of perfomance on processing time, and packet generaration; and the methods to improove the realism of the traffic generated. In the is we believe to overcome the current limitations.
